method

### 2022-02-07 06_Paper/ER-ED/method.Rmd
Update method.Rmd
fixed past tense

@@

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, "We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

The procedure described above was tested in a pilot study with ...

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task with the levels one to four.
Then, they completed an ED procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, took place exactly one week after session one.
Participants gave signed informed consent for the second session.
Afterwards the ER paradigm was conducted.
Participants first received written instructions on the ER paradigm and ER strategies that they should apply.
A training session was performed to ensure that all participants were able to implement the ER strategies.
Next, electrodes to measure EMG were attached and the ER paradigm was conducted. 
Participants received 30.00€ or course credit as compensation for participation.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

@@

The online survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

@@

The ER paradigm roughly consisted of three parts that will be described in the following.

*Part one: ER task.* <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

*Part two: ER effort discounting.* <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, we added an initial comparison that began with the option "1 EUR for strategy A or 1 EUR for strategy B".
The strategy that was not chosen was assigned the value 2 EUR.
From this point on, comparisons between strategies followed the original COG-ED paradigm [@Westbrook2013].
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

*Part three: ER choice.* <br>
After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
Importantly, there were no further instruction, on what basis they should make their decision.
Participants should make their decision freely, according to the criteria they considered important for themselves.
However, participants were asked to state the reasons for the decision afterwards.
As soon as they had decided, they saw the respective instruction. 
After, the block with another 20 negative pictures started.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using _G*Power_ [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.

>>>>

# import questionnaire df

data_quest = read.csv(here("04_RawData", "pilot", "ER-ED", "dfs", "df_quest.csv"), sep = ",")

@@

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants ()

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting. 
Before each session, participants receive information about the respective experimental procedure and provide informed consent. 
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level. <!--JZ: Hast du ED schon als Abkürzung eingeführt?-->
The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG are being attached and the ER paradigm is conducted. 
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

@@

The online survey contains a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] is used. 
Dispositional use of ER is assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017].
To assess Need for Cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] is used.
To assess self-control, sum scores of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

@@

The ER paradigm roughly consists of three parts that will be described in the following.

*Part one: ER task.* <br>
Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants are told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively. 
Every participant first has the condition "active viewing-neutral" that serves as a baseline condition.
During this block, 20 neutral pictures are presented.
Participants are asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewe negative pictures.
During the third, fourth, and fifth block, participants see negative pictures and are asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants are asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants are asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants are told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants are instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants receive written instruction and complete a training session.
After the training session, participants are asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) is randomized between participants.

*Part two: ER effort discounting.* <br>
In the second part, ER effort discounting takes place.
The procedure of the discounting follows the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
We use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values are presented.
The order of the comparisons is randomized.
Because there is no strategy that is objectively more difficult, we added an initial comparison that begins with the option "1 EUR for strategy A or 1 EUR for strategy B".
The strategy that is not chosen is assigned the value of 2 EUR.
From this point on, comparisons between strategies follow the original COG-ED paradigm [@Westbrook2013].
Participants are instructed to decide as realistically as possible, imagining the displayed money would really be up for election.

*Part three: ER choice.* <br>
After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there are no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to the criteria they consider important for themselves.
However, participants are asked to state the reasons for the decision afterwards.
As soon as they have decided, they see the respective instruction and the block with another 20 negative pictures starts.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. <!--JZ: Das stand oben schon mal-->
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using _G*Power_ [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.
